---
title       : An Analysis of the Bachelor Data
subtitle    : 
author      : 
job         : COMM 206 In-class Activity
logo        : bachelor.jpeg
framework   : io2012               # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js         # {highlight.js, prettify, highlight}
hitheme     : tomorrow             # 
widgets     : [mathjax, bootstrap, quiz] # {mathjax, quiz, bootstrap}
mode        : selfcontained        # {standalone, draft}
knit        : slidify::knit2slides
--- #DA

<style>
body {
  background-color: #000;
}
.quiz-option label{
  display: inline;
  font-size: 1em;
}
ul.nav li::before { content: ""; }  
ul.nav li{ font-size: 18px; line-height: 24px;}
</style>

```{r echo=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(message=FALSE, tidy=TRUE, warning=FALSE)
```

```{r echo=FALSE, message=FALSE}
# load packages and data
library(XLConnect)
library(dplyr)
library(tidyr)
library(magrittr)
library(slidify)
library(ggplot2)
wb <- loadWorkbook("~/Desktop/16W/COMM 206/data/Bachelor Data.xlsx")
dat <- readWorksheet(wb, sheet = 1)

# Data Cleaning
dat %<>% 
  separate(Date, c("start", "end", "year"), sep = "[–,]") %>% # separate dates
  mutate_each(funs(as.Date(., "%B %d")), c(start, end)) %>% # generate dates
  mutate(duration = as.numeric(end - start), 
         color.agree = Star.Hair.Color == Winner.Hair.Color) %>% # add duration and color.agree
  filter(Outcome %in%  c("Married", "Apart")) %>% # keep only these two levels
  select(-c(Col1, matches("star($|t|.o)"), end, Winner)) # select only the relevant columns
```

## Descriptive Analysis
### Collected Variables
```{r echo=FALSE}
wb <- loadWorkbook("~/Desktop/16W/COMM 206/data/Bachelor Data.xlsx")
dat2 <- readWorksheet(wb, sheet = 1)
names(dat2)[-1]
```
### Used Variables
```{r echo=FALSE}
names(dat)
```

--- #DA2
## Descriptive Analysis
### Proposal by Showtype
```{r echo=FALSE}
dat %>%
  group_by(Showtype, Proposal) %>% 
  summarise(n = n())
```

--- #DA3
## Descriptive Analysis
### Average Show Duration and Age of the Bachelor
```{r echo=FALSE}
dat %>% 
  group_by(Showtype, Proposal, Outcome) %>% 
  summarise(n = n(), avg.duration = mean(duration), avg.age = mean(Star.Age))
```

--- #DA4
## Correlations: Age and Show duration with Outcome
```{r echo=FALSE}
# formatting the variables
dat %>% 
  mutate_each(funs(as.factor), Showtype, Proposal, Outcome) %>%
  mutate_each(funs(as.numeric), c(Season, year, Star.Age, duration)) %>% 
  mutate_each(funs(as.logical), color.agree) -> dat3

# Correlations with Outcome
cor.vars <- c("Star.Age", "duration")
sapply(cor.vars, function(x){cor(dat3[, x], as.numeric(dat3$Outcome))})
```

--- #DA5
## Correlations: Age and Show duration with Proposal
```{r echo=FALSE}
# Correlations with Outcome
cor.vars <- c("Star.Age", "duration")
sapply(cor.vars, function(x){cor(dat3[, x], as.numeric(dat3$Proposal))})
```



